Staged Abstract Interpreter

### 2018-01-07 paper/paper.tex
update benchmarks
misc update

Application: for example, k-CFA (k > 0) is naturally a kind of whole program analysis, because 
it need the last k calling contexts as abstraction. But can we analyze programs (libraries) separately 
which generate the specialized analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.

@@

5. Show the evaluation result on benchmark programs (TODO: collect benchmark programs). 
Compare with normal abstract interpreter, 
abstract compilation\cite{Boucher:1996:ACN:647473.727587}, and OAAM \cite{Johnson:2013:OAA:2500365.2500604}.

>>>>

Application: for example, k-CFA (k > 0) is naturally a kind of whole program analysis,
because it is interpreter and need the last k calling contexts as abstraction. 
But can we analyze programs (libraries) separately which generate the specialized 
analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.

@@

5. Show the evaluation result on benchmark programs. 
Compare with normal abstract interpreter, 
abstract compilation\cite{Boucher:1996:ACN:647473.727587}, and OAAM \cite{Johnson:2013:OAA:2500365.2500604}.
Benchmarks and other reference implementations: \url{https://github.com/ilyasergey/reachability}.
